The Catalyst native network token is named KAT (in reference to Katal, the unit of catalyst activity). A KAT provides the network with the functionality to pay for network services or receive value for the provision of network services. It derives its intrinsic value from the development and use of the network and hence provides utility for both work undertaken by producer nodes and use of the network. \\

A Fulhame (FUL) is the smallest amount with KAT tokens, representing 0.0000000000001 KAT (a thousand billionth of a KAT token), named in homage to the chemist who invented the concept of catalysis, Elizabeth Fulhame.\\

KAT is a utility token and as such aims at providing Catalyst network users with access to services supported by dApps and Smart Contracts. The tokens are not designed as an investment although the value of the tokens can vary according to the demands for services on the network. These tokens are considered a medium of exchange as these can be used to facilitate the sale, purchase or trade of services on the network. Such trades take place via the use of transactions created by users and broadcast on the network. \\

The transfer of KAT tokens between user accounts are embedded in transactions. The transactions are processed by some nodes on the network (as discussed in section~\ref{Sec:PRT}) which are tasked with verifying said transactions and using these to produce a valid update to the balance of these accounts stored on the distributed ledger. The ledger database needs to be frequently and securely updated to account for these token transfers. A healthy network thus relies on a robust mechanism to manage the ledger database in a decentralised manner. Catalyst consensus-based protocol (Chapter~\ref{Cha:CM}) is implemented to incentivise users on the network to contribute to the ledger database management, offering them tokens as reward for their work. This reward typically comprises two components: a) tokens paid by the users issuing transactions and directly debited from their accounts, in the form of transaction fees; b) new tokens injected (or released) into the system. The token supply model adopted for Catalyst base currency (KAT tokens) is inflationary-based: the number of tokens injected into the system (annually) will be a fraction of the total amount of circulating tokens, adjusted to ensure a healthy and growing network. The economic considerations defining the token supply model of KAT tokens are beyond the scope of this document. 
