Nodes in the network receive and forward transactions to their peers. In order to prevent spamming attack over the network, nodes only forward transactions that are considered valid against a validity check list. Before forwarding it to its peers, a peer verifies the transaction against the following list of criteria:
 
\begin{itemize}
\item The transaction syntax (aforementioned in \ref{Sec:TStru}) and data structure must be correct.
\item The transaction size in bytes is greater than or equal to 160 Bytes (defined by the parameter MIN\_STD\_SIZE for non-confidential transaction) or 800 Bytes (defined by the parameter MIN\_CON\_SIZE for confidential transaction).
\item The transaction size in bytes is less than 1 Mbyte (defined by the parameter MAX\_STD\_SIZE or MAX\_CON\_SIZE depending on the transaction type).
\item The transaction list of entries must have at least two elements, each element must have a correct syntax. 

For non-confidential transaction $E_i$ must have a total size of 48-byte and 3 components:
\begin{itemize}
\item A public key $Q_i$ with a corresponding account address $A_i$ stored on the ledger where the account have a visible balance (8-byte field).
\item An amount $v_i^t$ that once added to the balance $v_i$ of the account mapped with the public key leaves the account balance positive ($v_i+v_i^t > 0$)
\end{itemize}
For confidential transaction $E_i$ must have a total size of 742-byte and 4 components:

\begin{itemize}
\item A public key $Q_i$ with a corresponding account address $A_i$ stored on the ledger where the account has an hidden balance (32-byte field).
\item A 32-byte PC $C_i^t$ 
\item A 672-byte range proof must validate against a new PC built out of the sum of $C_i^t$ and the account balance $C_i$. 
\end{itemize}

\item The transaction fee amount $v^f$ is greater than a (positive) minimum fee values MIN\_TX\_FEE
\item The relation $\sum_{i=1}^{n}v^t_i + v^f = 0$ must be verified for non-confidential transaction.
\item The transaction signature must validate against the public key built out of the public keys stored in the transaction entries 
\end{itemize}

The verification of the range proofs in the transaction is costly in computer resources, and is therefore only performed by the producers. 